---
title: "HomeworkWeek6"
output: html_document
---

## Get Data within R (notebook)  
  
### In the computer terminal, using the command "wget" to get the data. There will be a file called "gene_dist_head.tsv.gz" in the home directory.  
  
### Unzip the file, and there will be a file called "gene_dist_head.tsv" in the home directory.  

### Open RStudio  
  
### Set the working directory  
  
```{r}
setwd('/Users/Liu/')
```

### Install Packages  
  
```{r}
install.packages("ggplot2")
install.packages("plotly")
```

### Load the .tsv data into a dataframe in RStudio and load in libraries  
  
```{r}
{
  mygenes <- read.table(file = 'gene_dist_head.tsv',header = TRUE, sep = '\t')
  library(ggplot2)
  library(plotly)
}
```

## Summary the data  
  
```{r}
summary(mygenes)
```

### Put the summary into a data frame  
  
```{r}
summary_mygenes <- summary(mygenes)
```

### Refer to the labels such as: mygenes$feature where the $ sign indicates referring to a column.  
  
### Get info about the column names or row names  
  
```{r}
colnames(mygenes)
rownames(mygenes)
```

### Subset data  
  
```{r}
mygenes[,c(2,4)]
```

### Get a vector which tells what rows match something  
  
```{r}
mygenes[mygenes$chr==1,c(1,2,3,4,5)]
```

### Find out how many categories are in categorical data  
  
```{r}
levels(mygenes$chr)
```

## Create a subset, and put X as the chromosomes, and plot in ggplot  
  
```{r}
#Make sure to load in libraries
#library(ggplot2)  
#library(plotly)
# We define a factor set of autosomes
autosomes<-c("1","2","3","4","5","6","7","8","9","10",
 "11","12","13","14","15","16","17","18","19","20","21","22")  
# We create a new dataframe called 'genes' which only has autosomes, however we still have those additional factors
genes<- mygenes[ which(mygenes$chr %in% autosomes), ] 
# We remove the factors and then order them so they are numerical order and not alphabetical
genes$chr <- factor(genes$chr, levels = autosomes) 
 # We plot in ggplot 
ggplot(data = genes) +  geom_bar(mapping = aes(x = chr, fill = feature), width = 1)
```

## Plot to polar coordinates  
  
```{r}
ggplot(data = genes) +
 geom_bar(mapping = aes(x = chr, fill = feature), width = 1) +
 coord_polar()
```

## Create interactive graph  
  
### Go back to the original non-polar version  
  
### Using the plotly library and ggplotly  
  
```{r}
mygenes_interactive <- ggplot(data = genes) + geom_bar(mapping = aes(x = chr, fill = feature), width = 1)
ggplotly(mygenes_interactive)
```

## Done!  